No proof nets for MLL with units\\[5pt]\Large Proof equivalence in MLL is \textsc{pspace}-complete

### 2014-01-18 main/LICS.tex
re-wrote defn. "standard linking" (was: "natural linking")

\smallskip
A \emph{reconfiguration step} $\gamma\perm*\delta$ relates two (partial) configurations for an \textsc{ncg} $G$ that differ in value (or definedness) on exactly one edge.
%
\end{definition}

\emph{Non-deterministic constraint graph reconfiguration} or \emph{\textsc{ncg}-reconfiguration} is the problem of deciding when two configurations for a constraint graph are connected in the graph of total configurations and reconfiguration steps.
%
\emph{Partial \textsc{ncg}-reconfiguration} is the same problem for partial configurations.

%\emph{(Partial) \textsc{ncg}-reconfiguration} is the problem of deciding when two (partial) configurations are connected by a path in the graph of (partial) configurations and reconfiguration steps.

@@

\begin{proposition}
Partial \textsc{ncg}-reconfiguration is \textsc{pspace}-complete.
\end{proposition}

\begin{IEEEproof}
Partial \textsc{ncg}-reconfiguration simulates \textsc{ncg}-reconfiguration:
%
%There is a path between total configurations $\gamma$ and $\delta$ in partial \textsc{ncg}-reconfiguration if and only if there is one in \textsc{ncg}-reconfiguration, for the following two reasons.
%
firstly, if $\gamma\perm*\delta$ for partial configurations, then these may be completed to total configurations $\gamma'\perm*\delta'$ or $\gamma'=\delta'$; secondly,
%
if $\gamma'$ and $\gamma''$ are total configurations that both agree with a partial configuration $\gamma$ where it is defined, then $\gamma'$ and $\gamma''$ are connected in \textsc{ncg}-reconfiguration by reversing the edges on which they disagree.
%
\end{IEEEproof}

@@

The basis of the encoding of constraint graphs in MLL is formed by \emph{weight elements}, which encode one unit of weight on an edge, and \emph{constraint elements}, that encode one unit towards the inflow constraint of a vertex.
%
The arithmetic of linking formulae of the form $\bigtn(\bot^n)$ to formulae $\bigparr(1^m)$ will be used to ensure that a weight element may be linked to only two vertices.
%
Below left is a weight element, below right a constraint element.
\[
\begin{tikzpicture}[x=5mm,y=5mm,octo]
	\node[big_] (A) at (0,0) {$i'$}; 
	\node[big_] (B) at (2,0) {$j'$};
	\node[big_] (C) at (4,0) {$k'$};
	\draw[rounded corners] (-1,-1) rectangle (5,1);
\end{tikzpicture}
\qquad\qquad
\begin{tikzpicture}[x=5mm,y=5mm,octo]
	\node[big1] (1) at (0,0) {$m'$}; 
	\node[big1] (2) at (3,0) {$n'$};
	\draw[rounded corners] (-1,-1) rectangle (1,1) (2,-1) rectangle (4,1);
	\draw (1,0)--(2,0);
\end{tikzpicture}
\]
Throughout an encoding, the sum $i+j+k=m+n$ will be constant---this way, a priori any weight element may connect to any constraint element.
%
The value of $m$ (and thus $n$) will differ for each vertex.
%
The weight element above will be able to connect naturally to those constraint elements where $m=i$ and where $m=i+j$, as illustrated below.
\[
	\connectingElements 1 \qquad \connectingElements 2
\]
To ensure that no other connections can be made, values are chosen such that $m\bmod3=1$ and $n\bmod3=2$, and accordingly $i\bmod3=1$, $j\bmod3=0$, and $k\bmod3=2$.

@@

\begin{definition}
\label{def:graph encoding}
The \emph{encoding} $\itn G$ of an \textsc{ncg} $G=(V,E,c,v,w)$ is a sequent constructed as follows.
%
Let $V=\{v_1,\dotsc,v_n\}$ and $E=\{e_1,\dotsc,e_m\}$ where $|V|=n$ and $|E|=m$.

The encoding of a vertex $v_k$ is the formula
\[
	\itn{v_k} = \bigparr\big(C^{m\times c(v_k)} \big)\parr 1
\]
where each \emph{constraint element} $C$ is the formula
\[
	C = \bigparr\big(1^{3k+2}\big) \tn \bigparr\big(1^{3(n-k)+3}\big)
\]

The encoding of an edge $e$ connecting vertices $v_i$ and $v_j$ with $i<j$ is the formula
\[
	\itn{e} = \bigtn\big(W^{m\times w(e)}\big)\tn\bot
\]
where each \emph{weight element} $W$ is the formula
\[
	W = \bigtn\big(\bot^{3i+2}\big)\parr\bigtn\big(\bot^{3(j-i)+1}\big)\parr\bigtn\big(\bot^{3(n-j)+3}\big)
\]

The encoding of the graph $G$ is the sequent
\[
	%\itn G = \bigtn_{1\leq i\leq n}\itn{v_i}, \itn{e_1},\dotsc,\itn{e_k}, \bot^m
	\itn G = \itn{v_1}\tn\dotso\tn\itn{v_n}, \itn{e_1},\dotsc,\itn{e_m}, 1^p
\]
where $p=m\times(|w|-|c|)\times(3n+4)$; the $p$ instances of $1$ are called \emph{edge-absorbers}.

@@

In an \textsc{ncg} $G$, a vertex $v$ and an edge $e$ will be called \emph{appropriate} (for each other) if $v\in v(e)$, and \emph{inappropriate} otherwise.
%
This notion is extended to vertex-gadgets $\itn v$ and edge-gadgets $\itn e$ in $\itn G$.

For a weight element $W$ of an edge connecting $v_i$ and $v_j$, let the $\bot$-occurrences be named as follows,
\[
	W = \begin{array}[t]{l}
				 \big(\named{    \dagger}\bot\tn\named{   1}\bot\tn\dotsc\tn\named{3i+1}\bot\big) 
	~\parr\\[5pt] \big(\named{   \ddagger}\bot\tn\named{3i+2}\bot\tn\dotsc\tn\named{3j+1}\bot\big)
	~\parr\\[5pt] \big(\named{\downdagger}\bot\tn\named{3j+2}\bot\tn\dotsc\tn\named{3n+3}\bot\big)
	\end{array}
\]
and the $1$-occurrences of a constraint element $C$ in $\itn{v_k}$,
\[
	C = \big(\named{\alt    \dagger}1\parr\named{\alt{   1}}1\parr\dotso\parr\named{\alt{3k+1}}1\big)
	\tn \big(\named{\alt\downdagger}1\parr\named{\alt{3k+2}}1\parr\dotso\parr\named{\alt{3n+3}}1\big)~.
\]
There is a \emph{natural linking} for the sequent $W,C$ if $e$ is appropriate for $v_k$, i.e.\ if $k=i$ or $k=j$, as follows:
\[
	\links(x) = \alt x \qquad \text{for }x\in\{\dagger,\downdagger\}\cup\mathbb N
\]
\[
	\links(\ddagger)=
	\begin{cases}
		\alt	\dagger & \text{if }k=i \\
		\alt\downdagger & \text{if }k=j~.
	\end{cases}
\]
There is also a natural linking for the sequent $W,\named\star 1,\named{\alt 1}1,\dotsc,\named{\alt {3n+3}}1$ consisting of the weight element $W$ and $3n+4$ edge-absorbers:
\[
	\links(x)=
	\begin{cases}
		\star  & \text{if }x\in\{\dagger,\ddagger,\downdagger\} \\
		\alt x & \text{otherwise }.
	\end{cases}
\]

\begin{proposition}
\label{prop:element linkings}
\begin{enumerate}
	\item
Given a vertex $v$ and an appropriate edge $e$, for a constraint element $C$ in $\itn v$ and a weight element $W$ in $\itn e$ the natural linking for the sequent $W,C$ is a proof net.
	\item
Given a weight element $W$ for a graph with $|V|=n$, the natural linking for the sequent $W,1^{3n+4}$ is a proof net.
\end{enumerate}
\end{proposition}

The rightmost $1$-occurrence of each vertex-gadget $\itn v$, named $\alt v$ below, and the rightmost $\bot$-occurrence of each edge-gadget $\itn e$, named $\alt e$, will be called the \emph{indicator vertices} of $\itn v$ and $\itn e$.
%
% NOW: /indicator/ for edges and /indicator target/ for vertices
%
\[	
	\itn v = C\parr\dotso\parr C\parr \named{\alt v}1 \qquad \itn e= W\tn\dotso\tn W\tn\named{\alt e}\bot~.
\]

\begin{definition}
\label{def:configuration encoding}
The \emph{encoding} $\itn\gamma$ of a total configuration $\gamma$ for a graph $G$ is a linking $\links$ constructed incrementally, for each successive edge $e$, and for each successive weight element $W$ within $e$, as follows.
%
Let $\gamma(e)=v$; firstly, the the indicator vertex of $\itn e$ links to the indicator of $\itn v$.
%
Then successively for each weight element $W$ in $e$, if $\itn v$ has a first free constraint element $C$, extend $\itn\gamma$ to include the natural linking on $W,C$; otherwise, extend $\itn\gamma$ by the natural linking on the sequent consisting of $W$ plus the first $3n+4$ free edge absorbers.
\end{definition}

@@

\begin{IEEEproof}
Using Proposition~\ref{prop:scoping correctness}, it is sufficient to give a suitable scope for each $\parr$. 
%
The scope of each weight element $W$ is the sequent $W,C$ or $W,1^{3n+4}$ of its natural linking, which forms a proof net by Proposition~\ref{prop:element linkings}.
%
The scope of each vertex-gadget $\itn v$ contains the edge-gadgets $\itn e$ such that $\gamma(e)=v$, plus all the edge-absorbers within scopes of weight elements inside $\itn e$.
%
Since the weights of the connected edges $e$ sum to more than the inflow constraint of $v$, there are no unused constraint elements remaining in $\itn v$.
%
After contracting the scope of each $W$, each edge-gadget in the scope of $\itn v$ becomes a single string of connected vertices, connected to other edge-gadgets only via the special $\named v1$ of $\itn v$, thus forming a tree.
\end{IEEEproof}

@@

\begin{IEEEproof}
Let $W_i=A\parr B\parr C$, $W_j=D\parr E\parr F$, and $C=X\tn Y$.
%
We will illustrate the path of permutations for the case where $A,B,X$ and $D,X$, and thus also $C,Y$ and $E,F,Y$, are balanced sequents; other cases are similar.
%
\begin{enumerate}
	\item
The initial configuration is illustrated below; other weight and constraint elements are omitted, and $v$, $i$, and $j$ are the indicator vertices of $\itn v$, $\itn{e_i}$, and $\itn{e_j}$ respectively.
\NoIndent{
\[
	\octorollA1
\]
}
	\item
The link $i-v$ is re-attached to connect to an edge-absorber together with only the links from the first $\bot$ of each of $D$, $E$, and $F$. 
\NoIndent{
\[
	\octorollB2
\]
}
	\item
Secondly, the link from the first $\bot$ of $D$ is moved to $X$, and those of $E$ and $F$ are moved to $Y$.
\NoIndent{
\[
	\octorollB3
\]
}
	\item\label{item:exchange added}
There are subnets over the sub-sequents $A,B,X,D,\bot^m$ and $C,Y,E,F,\bot^k$.
%
These subnets may be rewired so that $D\parr E\parr F$ is naturally linked to $X\tn Y$: by Proposition~\ref{prop:parity determines equivalence}, the resulting subnets are equivalent as long as their parity is preserved.
%
Two links from $C$ to $X$ should remain exchanged, compared to the natural linking, for step \ref{item:exchange needed} below.
%
The links of $A,B,C$ connect to the edge-absorbers $\bot^m$ and $\bot^k$, with one remaining link from $B$ to $X$ and one from $C$ to $Y$.
\NoIndent{
\[
	\octorollC
\]
}
	\item
The link from $C$ to $Y$ is moved towards an edge-absorber connected to $A,B$.
\NoIndent{
\[
	\octorollD1
\]
}
	\item\label{item:exchange needed}
The link from $B$ to $X$ is the one remaining connection between the edge-gadgets $\itn{e_i}$ and $\itn{e_j}$.
%
Lemma~\ref{lem:double exchange} allows to swap the targets of the link from $B$ to $X$ and the link from $i$, and simultaneously undo the exchange in the links from $C$ to $X$ added in step \ref{item:exchange added} above.
\NoIndent{
\[
	\octorollD2
\]
}
	\item
The link from $i$ may be re-attached to $v$ to yield the final configuration.
\NoIndent{
\[
	\octorollA2
\]
}
\end{enumerate}
\end{IEEEproof}

>>>>

\smallskip
A \emph{reconfiguration step} $\gamma\perm*\delta$ relates two (partial) configurations for an \textsc{ncg} $G$ that differ in value (or definedness) on exactly one edge.
%
The reflexive--transitive closure of $(\perm*)$ will be denoted $(\perm)$.
%
\end{definition}

\begin{proposition}
\label{prop:partial simulates total reconfiguration}
For total configurations $\gamma$ and $\delta$, if $\gamma\perm\delta$ then $\gamma$ and $\delta$ are also connected by a sequence of reconfiguration steps over total configurations only.
\end{proposition}

\begin{IEEEproof}
By the following two observations: firstly, 
%
if $\gamma\perm*\delta$ for partial configurations, then these may be completed to total configurations $\gamma'\perm*\delta'$ or $\gamma'=\delta'$; and secondly,
%
if $\gamma'$ and $\gamma''$ are total configurations that both agree with a partial configuration $\gamma$ where the latter is defined, then $\gamma'$ and $\gamma''$ are connected by reversing the edges on which they disagree one after another.
%
\end{IEEEproof}

%
\emph{Non-deterministic constraint graph reconfiguration} or \emph{\textsc{ncg}-reconfiguration} is the problem of deciding when two configurations for a constraint graph are connected in the graph of total configurations and reconfiguration steps.
%
\emph{Partial \textsc{ncg}-reconfiguration} is the same problem for partial configurations.

@@

By Proposition~\ref{prop:partial simulates total reconfiguration} the following is then immediate.

\begin{proposition}
Partial \textsc{ncg}-reconfiguration is \textsc{pspace}-complete.
%\textsc{pncg}-reconfiguration is \textsc{pspace}-complete.
\end{proposition}

We will demonstrate the \textsc{pspace}-hardness of MLL proof equivalence by an encoding of partial \textsc{ncg}-reconfiguration in MLL.

@@

The basis of the encoding of constraint graphs in MLL is formed by \emph{weight elements}, which encode one unit of weight on an edge, and \emph{constraint elements}, that encode one unit towards the inflow constraint of a vertex.
%
The arithmetic of linking formulae of the form $\bigtn(\bot^n)$ to formulae $\bigparr(1^m)$ will be used to ensure that a weight element may be linked to only two vertices.
%
Below left is a weight element, below right a constraint element.
\[
\begin{tikzpicture}[x=5mm,y=5mm,octo]
	\node[big_] (A) at (0,0) {$i'$}; 
	\node[big_] (B) at (2,0) {$j'$};
	\node[big_] (C) at (4,0) {$k'$};
	\draw[rounded corners] (-1,-1) rectangle (5,1);
\end{tikzpicture}
\qquad\qquad
\begin{tikzpicture}[x=5mm,y=5mm,octo]
	\node[big1] (1) at (0,0) {$m'$}; 
	\node[big1] (2) at (3,0) {$n'$};
	\draw[rounded corners] (-1,-1) rectangle (1,1) (2,-1) rectangle (4,1);
	\draw (1,0)--(2,0);
\end{tikzpicture}
\]
For all edges and vertices in the encoding of a constraint graph, the sum $i+j+k=m+n$ will be the same---this way, a priori any weight element may connect to any constraint element.
%
The value of $m$ (and thus $n$) will differ for each vertex.
%
The weight element above will be able to connect naturally to those constraint elements where $m=i$ and where $m=i+j$, as illustrated below.
\[
	\connectingElements 1 \qquad \connectingElements 2
\]
To ensure that no other connections can be made, values are chosen such that $m\bmod3=1$ and $n\bmod3=2$, and accordingly $i\bmod3=1$, $j\bmod3=0$, and $k\bmod3=2$.

@@

\begin{definition}
\label{def:graph encoding}
The \emph{encoding} $\itn G$ of a constraint graph $G=(V,E,c,v,w)$ is a sequent constructed as follows.
%
Let $V=\{v_1,\dotsc,v_n\}$ and $E=\{e_1,\dotsc,e_m\}$ where $|V|=n$ and $|E|=m$.

\noindent
The encoding of a vertex $v_k$ is the formula
\[
	\itn{v_k} = \bigparr\big(C_n(k)^{m\times c(v_k)} \big)\parr\1
\]
where each \emph{constraint element} $C_n(k)$ is the formula
\[
	C_n(k) = \bigparr\big(1^{3k+2}\big) \tn \bigparr\big(1^{3(n-k)+3}\big)
\]

\noindent
The encoding of an edge $e$ connecting vertices $v_i$ and $v_j$ with $i<j$ is the formula
\[
	\itn{e} = \bigtn\big(W_n(i,j)^{m\times w(e)}\big)\tn\bot
\]
where each \emph{weight element} $W_n(i,j)$ is the formula
\[
	W_n(i,j) = \bigtn\big(\bot^{3i+2}\big)\parr\bigtn\big(\bot^{3(j-i)+1}\big)\parr\bigtn\big(\bot^{3(n-j)+3}\big)
\]

\noindent
The encoding of the graph $G$ is the sequent
\[
	\itn G = \itn{v_1}\tn\dotso\tn\itn{v_n}, \itn{e_1},\dotsc,\itn{e_m}, 1^p
\]
where $p=m\times(|w|-|c|)\times(3n+4)$.

@@

In the above definition, the final $\1$-subformula of a vertex-gadget $\itn{v_k}$ is its \emph{indicator target}; the final $\bot$-subformula of an edge-gadget $\itn{e}$ is its \emph{indicator}; and in the completed encoding $\itn G$ the $p$ instances of $\1$ are the \emph{edge-absorbers}.
%
In a constraint graph $G$, a vertex $v$ and an edge $e$ will be called \emph{appropriate} (for each other) if $v\in v(e)$, and \emph{inappropriate} otherwise.
%
This notion is extended to vertex-gadgets $\itn v$ and edge-gadgets $\itn e$ in $\itn G$, and their respective constraint elements and weight elements.

A configuration $\gamma$ for a constraint graph $G$ will be encoded as a proof net for the sequent $\itn G$.
%
Firstly we will define a standard way of linking a weight element to a constraint element.

\begin{definition}
\label{def:standard linkings}
For a weight element $W=W_n(i,j)=A\parr B\parr C$,
\begin{enumerate}
	\item
for a constraint element $C=C_n(i)=X\tn Y$, the \emph{standard linking} for the sequent $W,C$ links the first $\bot$ in $A$ to the first $\1$ in $X$, the first $\bot$ in $B$ and $C$ each to the first $\1$ in $Y$, and the remaining $\bot$-occurrences in $A,B,C$ to the remaining $\1$-occurrences in $X,Y$;
	\item
for $C=C_n(j)=X\tn Y$, the \emph{standard linking} for $W,C$ is defined as above, except the first $\bot$ in $B$ links to the first $\1$ in $X$;
	\item
the \emph{standard linking} for the sequent $W,\1^{3n+4}$ links the first $\bot$ in $A$, $B$, and $C$ each to the first $\1$, and the remaining $\bot$-occurrences to the remaining $\1$-occurrences.
\end{enumerate}
\end{definition}

The standard linkings defined in the first and third case of the above definition are illustrated below.

\begin{tikzpicture}[x=5mm,y=5mm,octo]
	\node[circ] (1) at (-.25,0) {};
	\node[big1] (2) at (1,0) {};
	\node[big1] (3) at (2.5,0) {};
	\node[big1] (4) at (5.5,0) {};
	\draw[rounded corners] (-1,-1) rectangle (3.5,1) (4.5,-1) rectangle (6.5,1);
	\draw (3.5,0)--(4.5,0);
	%
	\draw (-.25,4) node[bullet] (a) {} -- (.75,4) node[big_] (A) {};
	\draw (2.25,4) node[bullet] (b) {} -- (3.25,4) node[big_] (B) {};
	\node[big_] (C) at (5.5,4) {};
	\draw[rounded corners] (-1,3) rectangle (6.5,5);
	%
	\begin{scope}[thepink,->]
		\draw[bend right=5] (a) to (1);
		\draw[bend right=10] (b) to (1);
		\draw[big>,bend left=25] (A) to (2);
		\draw[big>,bend left=20] (B) to (3);
		\draw[big>,bend left=15] (C) to (4);
	\end{scope}
\end{tikzpicture}
\qquad
\begin{tikzpicture}[x=5mm,y=5mm,octo]
	\node[circ] (1) at (.75,0) {};
	\node[big1] (2) at (2,0) {};
	\node[big1] (3) at (3.5,0) {};
	\node[big1] (4) at (5,0) {};
	%
	\draw ( 0  ,4) node[bullet] (a) {} -- ( 1  ,4) node[big_] (A) {};
	\draw ( 2.5,4) node[bullet] (b) {} -- ( 3.5,4) node[big_] (B) {};
	\draw ( 5  ,4) node[bullet] (c) {} -- ( 6  ,4) node[big_] (C) {};
	\draw[rounded corners] (-.5,3) rectangle (7,5);
	\path (0,-1) -- (1,-1);
	%
	\begin{scope}[thepink,->]
		\draw[bend right=5] (a) to (1);
		\draw[bend right=10] (b) to (1);
		\draw[bend right=15] (c) to (1);
		\draw[big>,bend left=25] (A) to (2);
		\draw[big>,bend left=20] (B) to (3);
		\draw[big>,bend left=15] (C) to (4);
	\end{scope}
\end{tikzpicture}

\begin{proposition}
\label{prop:element linkings}
The standard linkings of Definition~\ref{def:standard linkings} are proof nets.
\end{proposition}

The encoding of a configuration is then as follows.

\begin{definition}
\label{def:configuration encoding}
The \emph{encoding} $\itn\gamma$ of a total configuration $\gamma$ for a constraint graph $G$ is a linking $\links$ for $\itn G$, constructed incrementally for each successive edge $e$ and for each successive weight element $W$ within $e$, as follows.
%
Let $\gamma(e)=v$; firstly, the indicator of $\itn e$ is linked to the indicator target of $\itn v$.
%
Then successively for each weight element $W$ in $e$, if $\itn v$ has a first free constraint element $C$, extend $\itn\gamma$ to include the standard linking on $W,C$; otherwise, extend $\itn\gamma$ by the standard linking on the sequent consisting of $W$ plus the first $3n+4$ free edge absorbers.
\end{definition}

@@

\begin{IEEEproof}
Using Proposition~\ref{prop:scoping correctness}, it is sufficient to give a suitable scope for each $\parr$. 
%
The scope of each weight element $W$ is the sequent $W,C$ or $W,1^{3n+4}$ of its standard linking, which forms a proof net by Proposition~\ref{prop:element linkings}.
%
The scope of each vertex-gadget $\itn v$ contains the edge-gadgets $\itn e$ such that $\gamma(e)=v$, plus all the edge-absorbers within scopes of weight elements inside $\itn e$.
%
Since the weights of the connected edges $e$ sum to more than the inflow constraint of $v$, there are no unused constraint elements remaining in $\itn v$.
%
After contracting the scope of each $W$, each edge-gadget in the scope of $\itn v$ becomes a single string of connected vertices, connected to other edge-gadgets only via the special $\named v1$ of $\itn v$, thus forming a tree.
\end{IEEEproof}

@@

\begin{IEEEproof}
Let $W_i=A\parr B\parr C$, $W_j=D\parr E\parr F$, and $C=X\tn Y$.
%
We will illustrate the path of permutations for the case where $A,B,X$ and $D,X$, and thus also $C,Y$ and $E,F,Y$, are balanced sequents; other cases are similar.
%
\begin{enumerate}
	\item
The initial configuration is illustrated below; other weight and constraint elements are omitted, and $v$, $i$, and $j$ are the indicator vertices of $\itn v$, $\itn{e_i}$, and $\itn{e_j}$ respectively.
\NoIndent{
\[
	\octorollA1
\]
}
	\item
The link $i-v$ is re-attached to connect to an edge-absorber together with only the links from the first $\bot$ of each of $D$, $E$, and $F$. 
\NoIndent{
\[
	\octorollB2
\]
}
	\item
Secondly, the link from the first $\bot$ of $D$ is moved to $X$, and those of $E$ and $F$ are moved to $Y$.
\NoIndent{
\[
	\octorollB3
\]
}
	\item\label{item:exchange added}
There are subnets over the sub-sequents $A,B,X,D,\bot^m$ and $C,Y,E,F,\bot^k$.
%
These subnets may be rewired so that $D\parr E\parr F$ is naturally linked to $X\tn Y$: by Proposition~\ref{prop:parity determines equivalence}, the resulting subnets are equivalent as long as their parity is preserved.
%
Two links from $C$ to $X$ should remain exchanged, compared to the standard linking, for step \ref{item:exchange needed} below.
%
The links of $A,B,C$ connect to the edge-absorbers $\bot^m$ and $\bot^k$, with one remaining link from $B$ to $X$ and one from $C$ to $Y$.
\NoIndent{
\[
	\octorollC
\]
}
	\item
The link from $C$ to $Y$ is moved towards an edge-absorber connected to $A,B$.
\NoIndent{
\[
	\octorollD1
\]
}
	\item\label{item:exchange needed}
The link from $B$ to $X$ is the one remaining connection between the edge-gadgets $\itn{e_i}$ and $\itn{e_j}$.
%
Lemma~\ref{lem:double exchange} allows to swap the targets of the link from $B$ to $X$ and the link from $i$, and simultaneously undo the exchange in the links from $C$ to $X$ added in step \ref{item:exchange added} above.
\NoIndent{
\[
	\octorollD2
\]
}
	\item
The link from $i$ may be re-attached to $v$ to yield the final configuration.
\NoIndent{
\[
	\octorollA2
\]
}
\end{enumerate}
\end{IEEEproof}
